%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Developer} % Job title
    {Payplug - Fintech Startup} % Organization
    {Paris, France} % Location
    {November 2015 – June 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Python development on payplug payment solution.}
        \item {Developed a micro service to handle customers and cards information.}
        \item {Fixed bug and developed functionality on payments micro services, and payplug interface modules.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Developer} % Job title
    {Makazi - Data Management Platform} % Organization
    {Paris, France} % Location
    {August 2015 – Novembre 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on the conception and development of a new Data Management Platform.}
        \item {Developed a data dispatcher using Scala/Akka/Kafka.}
        \item {Trained the developer team to the concept of functional programming, reactive programming, CQRS architecture, event sourcing and lambda architecture.}
        \item {Investigated production issues and data inconsistency using Apache Spark.}
        \item {Worked on the maintenance and evolution of the old Data Management Platform (introduce Gradles script)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Developer} % Job title
    {Smartjog Ymagis Logistics - DCP Delivery Platform} % Organization
    {Montrouge, France} % Location
    {July 2014 – July 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on the maintenance and improvement of Python modules to handle platform supervision and transfer management.}
        \item {Worked on the conception and development of a transfer platform using Scala and the Akka framework to manage the DCP satellite transfer system, which was based on a multicast delivery, on top of the transfer protocol; the software was needed to handle routes, priority, queue, and multicast exclusion.}
      \end{cvitems} 
    }

%---------------------------------------------------------
  \cventry
    {Lead Developer} % Job title
    {Arkena - Content Delivery System} % Organization
    {Ivry sur Seine, France} % Location
    {May 2009 - December 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintained and upgraded the Java/J2EE platform, integrate Spring, Hibernate, Maven, move it to a 3 tiers architecture, and add a tomcat cluster.}
        \item {Developed and maintained of a SOAP Webservice with Axis2.}
        \item {Developed module for the Front-office and the Back-office of Arkenna.}
        \item {Maintained and developed python module for the system managing the supervision, installation, deployment and configuration of the arkena customer’s network.}
        \item {Worked on failover and distributed load mechanism to handle the increasing charge issues.}
        \item {Worked on the Establishment of a transcoding platform using Celery, FFmpeg, with also a Rest Api using flask.}
        \item {Developed a workflow System capable of handling complex workflow situation and task chaining using Hazelcast and MongoDb.}
        \item {Integrated the Arkena server-less and cloud storage service based on Openstack Swift by creating new python component.}
        \item {Integrated logstash (log monitoring system)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Teaching assistant} % Job title
    {Epitech - Computer Science School} % Organization
    {Kremlin Bicêtre, France} % Location
    {November 2009 – November 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Teaching Assistant for Java and J2EE courses attended by 3rd and 4th years students.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Trainee} % Job title
    {Proxecom - Ecommerce Startup} % Organization
    {Paris, France} % Location
    {September 2008–May 2009} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed an e-commerce platform using Php/Mysql.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Contractor} % Job title
    {Photographes de France} % Organization
    {Villejuif, France} % Location
    {January 2008– May 2008} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed an image manipulation software, using Python/PIL.
The goal was to provide a tool to create automatics picture composition based on an xml template, pictures, and meta-data.}
        \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Trainee} % Job title
    {Photographes de France} % Organization
    {Villejuif, France} % Location
    {July 2007– December 2007} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed Intranet modules in Php.}
        \item {Servers maintenance and administration.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
